---
title: "Food Authentification"
output:
 github_document:
  html_preview: false
---

This repository contains codes and snakemake workflow for running food authentification using NGS amplicon data. This workflow processes fastqs files for 48 samples with 2 negative controls.



```{r library_calls, include=FALSE}
library(tidyverse)
library(readxl)
library(ggtext)
library(RColorBrewer)
library(xlsx)
library(formattable)
library(knitr)
```

### Dependencies:

-   [fastp 0.23.4](https://github.com/OpenGene/fastp)
-   [Kraken version 2.1.3](https://github.com/DerrickWood/kraken2)
-   [multiqc, version 1.16](https://github.com/MultiQC/MultiQC)
-   `r R.version.string`
    -   `tidyverse` (v. `r packageVersion("tidyverse")`)
    -   `readxl` (v. `r packageVersion("readxl")`)
    -   `rmarkdown` (v. `r packageVersion("rmarkdown")`)
    -   `ggtext` (v. `r packageVersion("ggtext")`)
    -   `RColorBrewer` (v. `r packageVersion("RColorBrewer")`)
    -   `formattable` (v. `r packageVersion("formattable")`)
    -   `knitr` (v. `r packageVersion("knitr")`)

### My computer

```{r sesion_info, echo=FALSE}
sessionInfo()
```